Visualization and analysis of probability distributions of large temporal data

### 2021-11-09 Rmd/00-c-declaration.Rmd
running after updating R to 4.1.2

```{r signature, out.width = "20%", fig.align = "left", eval = file.exists("img/signature.png")}
knitr::include_graphics("img/signature.png")
```

>>>>

```{r signature, out.width = "20%", fig.align = "left", eval = FALSE}
knitr::include_graphics("img/signature.png")
```

<!-- eval = file.exists("img/signature.png") -->
